Bayesian exponential random graph modeling of KWL Burial network

### 2020-12-13 analysis/paper/paper.Rmd

<!-- comparison between two networks using patchwork bootstrap --> 
One key difference between the pre-European and post-European networks is their size, with `r pre_E` burials compared to `r post_E` burials. To understand if this network size difference affects the posterior distributions, we conducted a sensitivity test by randomly removing `r diff_pre_post` nodes from the post-European network to resemble the size of pre-European network using a vertex bootstrap procedure. Vertex bootstrap is a non-parametric method that conducts resampling for all vertices (i.e. node) of a network to quantify standard errors in the network statistics of interest. This enables the evaluation of uncertainty for networks and the comparison between networks by examining their confidence intervals for the network population, especially for smaller networks. We set the resampling size to 1,000 networks to compute network statistics, including density, clustering, and degree, for our two networks. The result shows that the 95% confidence interval of each network statistic contains the observed network density and degree, but the observed network clustering values are higher than the 95% CI of the bootstrap distributions. This pattern is consistent before and after node removal for the post-European network. The bootstrap distributions for the post-European network, when adjusted to be the same size pre-European network, show distinct differences from the pre-European network statistics. This indicates our networks are relatively robust to differences in sample size, and suggests a negligible sample size effect.

>>>>

<!-- comparison between two networks using bootstrap --> 
One key difference between the pre-European and post-European networks is their size, with `r pre_E` burials compared to `r post_E` burials. To understand if this network size difference affects the posterior distributions, we conducted a sensitivity test by randomly removing `r diff_pre_post` nodes from the post-European network to resemble the size of pre-European network using a vertex bootstrap procedure. Vertex bootstrap is a non-parametric method that conducts resampling for all vertices (i.e. node) of a network to quantify standard errors in the network statistics of interest. This enables the evaluation of uncertainty for networks and the comparison between networks by examining their confidence intervals for the network population, especially for smaller networks. We set the resampling size to 1,000 networks to compute network statistics, including density, clustering, and degree, for our two networks. The result shows that the 95% confidence interval of each network statistic contains the observed network density and degree, but the observed network clustering values are higher than the 95% CI of the bootstrap distributions. This pattern is consistent before and after node removal for the post-European network. The bootstrap distributions for the post-European network, when adjusted to be the same size pre-European network, show distinct differences from the pre-European network statistics. This indicates our networks are relatively robust to differences in sample size, and suggests a negligible sample size effect.
